%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Ian Hutchinson} \\ \vspace{1pt}
    \small 908-380-1683 $|$ \href{mailto:ih6535@protonmail.com}{\underline{ih6535@protonmail.com}} $|$ 
    \href{https://www.linkedin.com/in/ian-hutchinson-3813b5157}{\underline{linkedin.com/in/ian}}
    % \href{https://github.com/...}{\underline{github.com/jake}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northrop Grumman}{Baltimore, Maryland}
      {Principal Software Engineer}{June 2022 -- Present}
      \resumeItemListStart
        \resumeItem{Led development and delivery of a large-scale multi-threaded C++20 application, coordinating engineering efforts across multiple organizations and customer teams.}
        \resumeItem{Architected and implemented a configurable, containerized software platform leveraging modern C++20, automated testing, GitLab CI/CD, Conan, and Linux-based deployment environments.}
        \resumeItem{Designed high-performance concurrent software systems emphasizing scalability, reliability, and maintainability in mission-critical environments.}
        \resumeItem{Modernized a legacy C++ codebase by eliminating technical debt, simplifying dependencies, improving software quality, and reducing long-term maintenance costs.}
        \resumeItem{Served as Scrum Master and technical lead, mentoring engineers, driving Agile execution, and coordinating cross-functional development efforts.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Software Engineer}{October 2019 -- May 2022}
      \resumeItemListStart
        \resumeItem{Developed high-performance real-time C++ software for mission-critical systems with strict latency, reliability, and throughput requirements.}
        \resumeItem{Implemented new system capabilities that improved processing efficiency and resource utilization across deployed software platforms.}
        \resumeItem{Integrated machine learning-based target recognition capabilities into production software systems, enabling automated classification and decision support.}
        \resumeItem{Collaborated with systems, hardware, and test teams to design, integrate, validate, and deploy complex software solutions.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Associate Software Engineer}{January 2019 -- September 2019}
      \resumeItemListStart
        \resumeItem{Developed embedded software for airborne radar systems supporting surveillance and reconnaissance missions.}
        \resumeItem{Implemented and tested C++ software components for real-time radar processing applications.}
        \resumeItem{Supported software integration, troubleshooting, and verification activities throughout the development lifecycle.}
      \resumeItemListEnd    

    \resumeSubheading
      {Siemens}{Atlanta, Georgia}
      {Engineering Leadership Development Program Internship}{May 2018 -- August 2018}
      \resumeItemListStart
        \resumeItem{Developed and commissioned PLC and HMI control systems for industrial manufacturing facilities, supporting automation and production operations.}
        \resumeItem{Collaborated with customers, technicians, and engineers to deploy and validate automation solutions in production environments.}
    \resumeItemListEnd

    \resumeSubheading
      {MSA -- The Safety Company}{Pittsburgh, Pennsylvania}
      {Electrical Engineering Co-Op}{January 2017 -- May 2017}
      \resumeItemListStart
        \resumeItem{Developed software for automated test fixtures used to validate industrial gas sensors against safety and performance requirements.}
        \resumeItem{Analyzed test data and collaborated with engineering teams to improve sensor validation and manufacturing processes.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, Georgia}
      {Master of Science in Computer Science}{January 2023 -- December 2026 (est.)}
    \resumeSubheading
      {Penn State University}{University Park, Pennsylvania}
      {Bachelor of Science in Electrical and Electronics Engineering}{August 2014 -- December 2018}
  \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}: C++, C, Python, Java, SQL, Bash \\
    \textbf{Architecture \& Systems}: Software Architecture, System Design, Distributed Systems, Concurrent Programming, Multithreading, Real-Time Systems, Object-Oriented Design \\
    \textbf{Development \& DevOps}: Linux, Git, GitLab CI/CD, Docker, Conan, Automated Testing, Continuous Integration, Agile/Scrum \\
    \textbf{Databases \& Libraries}: SQL, SQLite, Eigen, STL
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
